Bacterial Microbiome and Obesity Meta-analysis Supplemental

### 2016-02-19 Sze_ObesityMicrobiomeMeta_PeerJ_2016.Rmd
manuscript draft1 completed

>>>>

We also investigated how the different OTUs, classified to Ruminococcaceae, that were important for the classification of obese and non-obese based on the OOB AUC performed from each study performed when analyzed with RR [Figure S4].  There was no significant increase in RR based on the Ruminococcaceae OTU (RR = 0.98 (CI 0.63, 1.53), P-value = 0.9225).  Thus it would seem that although Ruminococcaceae is important for classification the directionality is study dependent [Figure S4].

### 2016-02-19 microbiomeAndobesitySupplemental.Rmd
manuscript draft1 completed

**In-Depth Overview of Search Strategy:**

@@

**A Comparison of 16S Amplicon Sequencing and Metaphlan2:**

@@

>>>>

###In-Depth Overview of Search Strategy:

@@

###A Comparison of 16S Amplicon Sequencing and Metaphlan2:

@@

###Supplemental Results:

```{r, echo=FALSE, message=FALSE, warning=FALSE}
#Load required packages
library(meta)
library(metafor) #This package is used mostly for the more in-depth graph

#Change working directory
setwd("C:/users/marc/Desktop/obesity2")

StudyNo <- c(1, 2, 3, 4, 5, 6, 7)
Study <- c("Baxter", "HMP", "Escobar", "Arumugam", "Turnbaugh", "Zupancic", "Wu")
Year <- c("2015", "2011", "2014", "2010", "2009", "2012", "2012")
Total <- c("n=172", "n=256", "n=30", "n=85", "n=146", "n=201", "n=58")
tpos <- c(36, 13, 7, 17, 22, 55, 2) #obese in low Rumi group
tneg <- c(59, 140, 8, 26, 56, 103, 37) #nonobese in low Rumi group
cpos <- c(11, 13, 3, 20, 25, 23, 3) #obese in high Rumi group
cneg <- c(66, 90, 12, 22, 43, 26, 16) #nonobese in high Rumi group
RR <- c(2.65, 0.67, 2.33, 0.83, 0.77, 0.74, 0.32)
low <- c(1.45, 0.33, 0.74, 0.51, 0.48, 0.51, 0.06)
high <- c(4.86, 1.39, 7.35, 1.35, 1.23, 1.07, 1.78)

numeric.data <-as.data.frame(cbind(tpos, tneg, cpos, cneg))
raw.overall <- as.data.frame(cbind(StudyNo, Study,Year, Total, numeric.data))

dat <- escalc(measure = "RR", ai = tpos, bi = tneg, ci = cpos, di = cneg, data=raw.overall, append=TRUE)
k <- length(dat$StudyNo)
dat.fm <- data.frame(study=factor(rep(1:k, each = 4)))
dat.fm$grp <- factor(rep(c("T", "T", "C", "C"), k), levels = c("T", "C"))
dat.fm$out <- factor(rep(c("+", "-", "+", "-"), k), levels = c("+", "-"))
dat.fm$freq <- with(raw.overall, c(rbind(tpos, tneg, cpos, cneg)))

#escalc(out ~ grp | study, weights = freq, data = dat.fm, measure = "RR")

#Used to generate the RE Model estimate based on all the studies
res <- rma(ai=tpos, bi=tneg, ci=cpos, di=cneg, data=raw.overall, measure="RR", slab=paste(Study, Year, Total, sep=", "), method="REML")

#To create a graph visualize the data
forest(res, at=log(c(0.01, 1, 10)), atransf=exp, xlab="RR of Obesity in high versus low Ruminococcaceae based on Median", cex=0.8)
par(font=2) #Switch to bold

text(7.4, 8.3, "Relative Risk [95% CI]", pos=2, cex=0.8)  
text(-8.0, 8.3, "Study, Year, and n", pos=4, cex=0.8)

**Figure S4: Forest Plot of the Relative Risk based on the Ruminococcaceae classified OTU.**
